Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
update model script and paper

```{r}
#| echo: false
#| warning: false
#| message: false
base_plot <- ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
  theme_classic() +
  labs(y = "Candidate Support (%)", x = "Date") 
#+  scale_x_date(date_labels = "%b %Y")  # 设置 x 轴只显示月份和年份

# 绘制候选人支持率的点图和光滑线
base_plot + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  theme(legend.position = "bottom")
```

@@

ggplot(data = president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name, group = candidate_name)) +
  geom_line(size = 1,alpha = 0.5) + 
  geom_point(size = 1) + # Add data point
  scale_color_manual(values = c("Donald Trump" = "pink", "Kamala Harris" = "lightblue")) + 
  labs(x = "State",
       y = "Support Percentage (%)") + # Add X-axis and Y-axis
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

In this Bayesian framework, we assume a normal distribution for poll results influenced by several predictors: end date, candidate name, sample size, and state. We denote $y_i$ as the percentage of votes for a candidate in a given poll, where $beta_i$ represents the candidate effect, $gamma_i$ reflects the influence of sample size, and $delta_i$ corresponds to the state effect.

@@

In this setup, the intercept $\alpha$ represents the baseline poll result, while each $\beta$ coefficient captures the specific influence of its associated predictor on the vote percentage. The variable $\text{state}_j$ accounts for effects attributed to different states, while $\text{end\_date}_{i}$ models temporal trends.

Priors are defined as follows: $alpha$ follows a normal distribution with a mean of 50 and a standard deviation of 10. Each of the $\beta$ and $\gamma$ parameters has a normal prior centered at 0 with a standard deviation of 2.5, indicating a mild assumption about their potential effects without introducing bias. The noise parameter $\sigma$ adheres to an exponential distribution, facilitating flexibility in the unexplained variation.

We run the model using the @citeR package of @rstanarm, focusing on how the vote percentage varies based on the predictors.

The complete model, summarizing the components, can be expressed as:

$$y_i \sim \text{Normal}\left(\beta_0 + \beta_1 \cdot \text{end\_date}_i + \sum_{k=1}^{K} \gamma_k B_k(\text{state}_j), \sigma^2\right)$$

In this expression, $y_i$ represents the predicted vote percentage for observation $i$, modeled as a function of the predictors, where the mean $\mu_i$ captures the expected percentage, and $\sigma$ reflects the variability.

@@

## Bayesian Priors

For Bayesian inference, we apply the following prior distributions:

- **Intercept prior**: A `Normal(50, 10)` prior is used for the intercept, reflecting a moderately informative belief that baseline support percentage falls within the plausible range (centered around 50% with a moderate spread).
- **Coefficients prior**: A `Normal(0, 2.5)` prior is assigned to each regression coefficient, which is weakly informative and allows flexibility without over-restricting the influence of predictors.

These priors are selected to strike a balance between allowing the data to inform estimates while providing regularization to prevent extreme parameter values. The priors are justified based on general expectations of support ranges and aim to avoid overfitting.

## Assumptions and Limitations

@@

2. **Normality of Errors**: It is assumed that the residuals (the differences between observed and predicted values) follow a normal distribution. This assumption is crucial for making valid inferences; violations can lead to incorrect conclusions and unreliable credible intervals.

@@

8. **Error Distribution**: The model presumes normally distributed residuals. Any deviation from this assumption may influence the validity of the inference. Diagnostic checks and posterior predictive checks are used to assess model fit and adherence to assumptions.

>>>>

@@

ggplot(data = president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name, group = candidate_name)) +
  #geom_line(size = 1,alpha = 0.5) + 
  geom_point(size = 1) + # Add data point
  geom_smooth(se = FALSE) + 
  scale_color_manual(values = c("Donald Trump" = "pink", "Kamala Harris" = "lightblue")) + 
  labs(x = "State",
       y = "Support Percentage (%)") + # Add X-axis and Y-axis
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "bottom")
```

@@

In this Bayesian framework, support level are modeled as normally distributed and influenced by several predictors: end date, candidate name, sample size, and state. The variable $y_i$ denotes the percentage of votes for a candidate in a specific poll, with $\beta_i$ representing the candidate effect, $\gamma_i$ reflecting the influence of sample size, and $\delta_i$ corresponding to the state effect. The intercept $\alpha$ indicates the baseline poll result, while each $\beta_i$ coefficient quantifies the influence of its associated predictor on the vote percentage. Additionally, the variable $\text{state}_j$ captures the effects attributed to different states, and $\text{end\_date}_{i}$ models temporal trends.

@@

Priors are defined as follows. For the intercept, a `Normal(50, 10)` distribution is utilized, reflecting a belief that the baseline support percentage is centered around 50% with moderate variability. This choice indicates a moderately informative prior that captures plausible ranges for the intercept. Each regression coefficient is assigned a `Normal(0, 2.5)` prior, which is weakly informative, allowing flexibility in parameter estimation while minimizing bias. These priors are selected to strike a balance between allowing the data to inform estimates and providing regularization to prevent extreme values and overfitting. The chosen priors are grounded in reasonable expectations regarding support ranges, aiming to enhance the robustness of the model.

Then, the complete model, summarizing the components, can be expressed as:

$$y_i \sim \text{Normal}\left(\alpha + \beta_1 \cdot \text{end\_date}_i + \beta_2 \cdot \text{candidate\_name}_i + \beta_3 \cdot \text{sample\_size}_i + \sum_{j=1}^{M} \gamma_j \cdot \text{state}_j, \sigma^2\right)$$

@@

## Assumptions of the Bayesian Models

@@

2. **Normality of Errors**: It is assumed that the residuals (the differences between observed and predicted values) follow a normal distribution. This assumption is crucial for making valid inferences; violations can lead to incorrect conclusions and unreliable credible intervals. Diagnostic checks and posterior predictive checks are used to assess model fit and adherence to assumptions.

@@
